Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-17 prop_iop.tex
prop_iop.tex \subsection{Convexity} Updating...

One possibility is that the definition of quantum convexity is too
weak to guarantee a convex quantum interval-valued probability measure
having a non-empty core. On one hand, the product of non-commuting
projectors is not a projector so equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
is unlikely to extended to non-commuting projectors~$P_{0}$ and
$P_{1}$. On the other hand, we haven't found a way to guarantee a
non-empty core if we only strength the condition on commuting projectors
as well. For example, classically, equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
is a special case of 
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
If a classical interval-valued probability measure~$\bar{\mu}$ satisfies
equation~(\ref{eq:Dempster-Shafer-game}) for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
then the left-end point of $\bar{\mu}$ is called a Dempster-Shafer
belief function. Equation~(\ref{eq:Dempster-Shafer-game}) could
be extended to the quantum case. However, example~\ref{ex:three-dimensional-three-value}
also satisfies the corresponding condition for quantum interval-valued
probability measure: 
\begin{equation}
\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
\end{equation}
for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
In another word, this kind of conditions cannot eliminate the situation
of empty core.

>>>>

One possibility is that the definition of quantum convexity is too
weak to guarantee a convex quantum interval-valued probability measure
having a non-empty core. On one hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
to non-commuting projectors~$P_{0}$ and $P_{1}$ is unlikely to
success because the product of non-commuting projectors is not a projector.
On the other hand, strengthening equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
among commuting projectors cannot guarantee a non-empty core as well
if we follow what people strengthen convexity classically. Equation~(\ref{eq:QuantumInterval-valuedProbability-Convex})
classically is a special case of 
\begin{equation}
\bar{\mu}'\left(\bigcup_{i=1}^{N}E_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}'\left(\bigcap_{i\in I}E_{i}\right)\label{eq:Dempster-Shafer-game}
\end{equation}
when $N=2$, where $\bar{\mu}'$ is a classical interval-valued probability
measure. If $\bar{\mu}'$ satisfies equation~(\ref{eq:Dempster-Shafer-game})
for all set of event~$\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$,
then the left-end point of $\bar{\mu}'$ is called a Dempster-Shafer
belief function. It is reasonable to call a quantum interval-valued
probability~$\bar{\mu}$ Dempster-Shafer if $\bar{\mu}$ satisfies
\begin{equation}
\bar{\mu}\left(\bigvee_{i=1}^{N}P_{i}\right)+\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is odd}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\subseteq\sum_{I\subseteq\left\{ 1,\ldots,N\right\} \textrm{ and }\left|I\right|\textrm{ is even}}\bar{\mu}\left(\prod_{i\in I}P_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game-quantum}
\end{equation}
for all set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events$.
However, the quantum interval-valued probability measure in example~\ref{ex:three-dimensional-three-value}
is Dempster-Shafer and has an empty core. In summary, it is unlikely
to guarantee a non-empty core by strengthening convexity.
